---
title: "Computational Reproducibility"
author: "Fred LaPolla"
date: "10/14/2020"
output: html_document
---

```{r setup, include=TRUE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown file

This file, an R Markdown lets you combine plain text, in the white spaces, and code chunks, in the gray. The text is not really code, but can be used to communicate, while the code chunks let you combine the actual analysis you are running alongside the results. This means someone can see exactly what you did to get your results.

To add a chunk either click on the green Insert button and choose R or hit Command + Option + i (Mac) or Ctrl + Alt + i (PC)

```{r}
3+3
```

## Homework

1) Create an R Project to pull this file from GitHub. 

Completed!

2) Please describe one of the ways that Wilson et. al. suggest is a good practice for computational reproducibility and how a tool like R can be used. Write your answer below.
Wilson et. al suggest many practices for good computational reproducibility. Beyond data management in Git, I want to focus on the "Software" section, specifically commenting code. R allows comments to be placed all throughout the code to not only explain what each line means but how it fits into the project as whole. It is important not to just to comment the occasional line, but to have full explanations and examples within your funciton so that users can understand how to implement it. #This is an example of a code comment. So simple!
3) Add a code chunk and find the square root of 4 to the 13th power. If you are unsure of what command to use, google it. 

```{r}
sqrt(4^13)
```


4) Push this homework to the GitHub repository for the homework. 

Completed!



